\Large \bf Uncovering Bugs in Distributed Storage Systems\\during Testing (not in Production!)

### 2015-09-22 experience.tex
minor updates

MigratingTable provides a \emph{virtual table} that has an interface similar to an ordinary \Azure table. This interface is named \texttt{IChainTable}. The virtual table is backed by a pair of \emph{old} and \emph{new} tables, which must implement \texttt{IChainTable}. A background \emph{migrator} job is responsible for transparently moving all data from the old table to the new table. Meanwhile, each read and write operation issued to the virtual table is translated to a sequence of reads and writes on the backend tables according to a protocol, which intends to guarantee that when multiple applications issue \emph{input} operations to virtual tables that are backed by the same old and new tables, the output is compliant with the specification of \texttt{IChainTable} for the combined \emph{input history} as if all the operations were done on a single table. The goal of using \psharp was to systematically test this property.

\textbf{Modeling and testing}.
The main challenge behind testing MigratingTable is that there are many possible input histories and that the system is highly concurrent. The developers could have chosen specific input histories to test, but they were not confident that this approach would be effective in catching bugs, especially because concurrency increases the potential for difficult-to-foresee interactions between seemingly independent parts of the code. Instead they took advantage of the simplicity and near-determinism of the \texttt{IChainTable} specification to write an in-memory reference implementation, called \texttt{SpecTable}, to which the output of MigratingTable on an arbitrary input history can be compared. Then the test could sample from a distribution that was defined over all possible input histories within certain bounds, so that under the \emph{small scope hypothesis} that any given bug in MigratingTable leads to incorrect output for at least one input history in the distribution, each iteration of the test would have a positive probability of detecting the bug.

The MigratingTable was instrumented to report the intended \emph{linearization point} of each input operation on the abstract, shared virtual table. This allows the test harness to keep a \emph{reference} \texttt{SpecTable} in sync with the virtual table by sending each operation to the reference table when the linearization point on the virtual table is reached. The output of the operation on the MigratingTable is then checked against its output on the reference table.

>>>>

\textbf{Specifics of the system}.
MigratingTable provides a \emph{virtual table} that has an interface similar to an ordinary \Azure table. This interface is named \texttt{IChainTable}. A virtual table is backed by an \emph{old} and a \emph{new} table, both of which implement \texttt{IChainTable}. A \emph{migrator} job is responsible for moving all data from the old table to the new table in the background. Meanwhile, each read and write operation issued to the virtual table is translated to a sequence of reads and writes on the backend tables according to a protocol, which intends to guarantee that when multiple applications issue \emph{input} operations to virtual tables that are backed by the same old and new tables, the output is compliant with the specification of \texttt{IChainTable} for the combined \emph{input history} as if all the operations were done on a single table. The goal of using \psharp was to systematically test this property.

\textbf{Testing approach}.
There are two main challenges behind testing MigratingTable: the system is highly concurrent; and there are many possible input histories. The developers could have chosen specific input histories to test, but they were not confident that this approach would be effective in catching bugs, especially because concurrency increases the potential for difficult-to-foresee interactions between seemingly independent parts of the code. Instead, they created an in-memory reference implementation of the \texttt{IChainTable} specification, called \texttt{SpecTable}, to which the MigratingTable output on an arbitrary input history can be compared.

The \psharp test harness \emph{samples from a distribution} that was defined over all possible input histories within certain bounds, so that under the \emph{small scope hypothesis} that any given bug in MigratingTable leads to incorrect output for at least one input history in the distribution, each iteration of the \psharp systematic testing engine would have a positive probability of detecting the bug.

\textbf{Modeling approach}.
The MigratingTable was instrumented to report the intended \emph{linearization point} of each input operation on the abstract, shared virtual table. This allows the test harness to keep a \emph{reference} \texttt{SpecTable} in sync with the virtual table by sending each operation to the reference table when the linearization point on the virtual table is reached. The output of the operation on the MigratingTable is then checked against its output on the reference table.
